SAT Competition 2020\tnoteref{title}

### 2021-02-03 paper/main.tex
add comp refs

\textcolor{red}{need to add refs to intro... none right now...}

From what was once mainly the archetypal intractable (in particular NP-complete) problem, propositional satisfiability 
(or Boolean satisfiability, SAT) has flourished in practice into a success story of modern computer science.
This is due to advances in SAT solvers, i.e., implementations of decision procedures for SAT, which form today a 
central computational tool for solving real-world problem instances of various kinds of NP-hard search and optimization problems.
With standardized input formats, readily-available APIs for incremental applications,
and certified proof logging and checking capabilities, applications of SAT solver technology
have branched from first breakthrough applications in automated planning, test pattern generation and hardware verification
to thousands of different application settings.

The success of SAT would not be possible without the persistent efforts of the SAT community to further develop the performance and robustness
of SAT solvers. The SAT Competition series, with a history dating back to early 90s, aims to support and provide further incentives 
for maintaining and furthering this progress. Organized yearly as an international open event, the SAT competitions (and their variants
in the form of SAT Races and SAT Challenge) have a consistent track record of receiving tens of solver submissions yearly, submitted
by the community at large for obtaining a snapshot of the current state-of-the-art in practical SAT solving. Alongside participating solvers,
the competition invites through open calls submissions of benchmark instances representing, in particular, new interesting applications 
scenarios of SAT solvers. Indeed, in addition to evaluating recently developed solvers, an important aspect of the SAT competition series is
to collect on a yearly basis new benchmark sets, consisting of instances from various different application settings, which together with benchmark sets from previous years constitute a standard dataset for use in research papers and SAT solver development.

This article focuses on the 2020 instantiation of the SAT competitions. 
To this end, we provide
a detailed account of SAT Competition 2020 in terms of organizational details, competition tracks,
participating solvers, benchmarks, and the empirical results from the competition.
In terms of competition tracks, two new tracks, namely the cloud track and an application-specific track, where introduced in 2020,
in addition to the already earlier established main, parallel, and incremental tracks; we
provide motivation and the new organizational details for both of these new tracks.
In terms of solvers, we provide an overview of solving strategies and other details implemented in the top-performing solvers
from the competition, complementing the individual solver descriptions available in the 2020 competition proceedings \cite{SC2020}.
 As for benchmarks, we describe how the 2020 benchmark sets were constructed for each of the competition tracks, with 
an overview of the benchmarks contributed to the 2020 competition.
In terms of empirical results we provide further analysis on the results going beyond the standard rankings provided
on the SAT competition web pages.\footnote{\url{https://satcompetition.github.io/2020/}}
Finally, we also provide a discussion on lessons learned and ideas for future editions of SAT competitions.

@@

One can see that the VBS solves all the instances that
were solved by at least one solver and solves each instance in the best observed time.
By quantifying how much each participating solver contributes
to the performance of the VBS, we may attempt to establish which
technology (as represented by the solvers) is the most important
(and to what degree) in the observed state of the art of SAT solving.
We came up with the following three related metrics conceptually derived
from the notion of VBS:
\begin{description}
\item[VBS1]
``The fastest takes it all'':
For each solver we count the number of times, it was the fastest to solve an instance.
\item[VBS2]
``Time aware, but proportional'':
A solver $S$ solving an instance $I$ in time $T^S_I$ accrues 
the following fraction of a point for solving $I$:
$T^\mathit{VBS}_I/T^S_I$, where $T^\mathit{VBS}_I$ is the solution time of the best solver on $I$.
\item[VBS3]
``Split the point for solving'':
We award each solver $S$ solving an instance $I$ the fraction $1/|\mathcal{S}_I|$ of points, where
$\mathcal{S}_I$ is the set of solvers solving $I$.
\end{description}
We remark that the sum of VBS1 points, as well as VBS3 points, computed across all the solvers
is equal to the number of instances solved by at least one solver (later denoted \emph{total}).
This is obvious for VBS1, as exactly one solver scores a point for solving an instance.
In the case of VBS3, where we discard the information about the solution times, 
we evenly split the one point reward for solving an instance to those solvers which were successful on it.

@@

Table~\ref{tab:vbsMainALL} renders the just described three metrics applied 
to the full results of the Main track. We can see that the respective leaderboards 
are generally dominated by \solver{Kissat} and its configurations.
VBS1 tells us that \solver{Kissat-unsat} was most often the fastest solver,
in particular on \SI{11.5}{\percent} of all the solved instances.

@@

Amusingly, as can be seen from the ``contributes'' column, the presence of \solver{f2trc-DL} in the schedule is not necessary.
% The following three lines could be skipped without much harm:
All the 15 instances this solver solves under 76 seconds were already covered by the preceding three solvers.
This result, however, does not signify a bug, as Z3 was not asked to produce a schedule with a minimal number of
participating solvers.
Indeed, allowing any other solver to run for the 76 ``wasted'' seconds would not increase the overall total.

>>>>

From what was once mainly the archetypal intractable (in particular NP-complete) problem, propositional satisfiability 
(or Boolean satisfiability, SAT) has flourished in practice into a success story of modern computer science~\cite{DBLP:series/faia/2009-185}.
This is due to advances in SAT solvers, i.e., implementations of decision procedures for SAT, which form today a 
central computational tool for solving real-world problem instances of various kinds of NP-hard search and optimization problems.
With standardized input formats, readily-available APIs for incremental applications,
and certified proof logging and checking capabilities, applications of SAT solver technology
have branched from first breakthrough applications in automated planning, test pattern generation and hardware verification
to thousands of different application settings.

The success of SAT would not be possible without the persistent efforts of the SAT community to further develop the performance and robustness
of SAT solvers. The SAT Competition series, with a history dating back to early 90s, aims to support and provide further incentives 
for maintaining and furthering this progress. Organized yearly as an international open event, the SAT competitions (and their variants
in the form of SAT Races and SAT Challenge)~\cite{DBLP:journals/amai/SimonBH05,DBLP:conf/sat/BerreS03,DBLP:conf/sat/BerreS04,DBLP:journals/aim/JarvisaloBRS12,DBLP:journals/ai/BalintBJS15,DBLP:conf/aaai/BalyoHJ17,DBLP:journals/jsat/HeuleJS19}
 have a consistent track record of receiving tens of solver submissions yearly, submitted
by the community at large for obtaining a snapshot of the current state-of-the-art in practical SAT solving. Alongside participating solvers,
the competition invites through open calls submissions of benchmark instances representing, in particular, new interesting applications 
scenarios of SAT solvers. Indeed, in addition to evaluating recently developed solvers, an important aspect of the SAT competition series is
to collect on a yearly basis new benchmark sets, consisting of instances from various different application settings, which together with benchmark sets from previous years constitute a standard dataset for use in research papers and SAT solver development.

This article focuses on the 2020 instantiation of the SAT competitions. 
To this end, we provide
a detailed account of SAT Competition 2020 in terms of organizational details, competition tracks,
participating solvers, benchmarks, and the empirical results from the competition.
In terms of competition tracks, two new tracks, namely the cloud track and an application-specific track, where introduced in 2020,
in addition to the already earlier established main, parallel, and incremental tracks; we
provide motivation and the new organizational details for both of these new tracks.
In terms of solvers, we provide an overview of solving strategies and other details implemented in the top-performing solvers
from the competition, complementing the individual solver descriptions available in the 2020 competition proceedings~\cite{SC2020}.
 As for benchmarks, we describe how the 2020 benchmark sets were constructed for each of the competition tracks, with 
an overview of the benchmarks contributed to the 2020 competition.
In terms of empirical results we provide further analysis on the results going beyond the standard rankings provided
on the SAT competition web pages.\footnote{\url{https://satcompetition.github.io/2020/}}
Finally, we also provide a discussion on lessons learned and ideas for future editions of SAT competitions.

@@

One can see that the VBS solves all the instances that
were solved by at least one solver and solves each instance in the best observed time.
By quantifying how much each participating solver contributes
to the performance of the VBS, we may attempt to establish which
technology (as represented by the solvers) is the most important
(and to what degree) in the observed state of the art of SAT solving.
We will here consider the following three related metrics conceptually derived
from the notion of VBS.
\begin{description}
\item[VBS1]
``The fastest takes it all'':
For each solver we count the number of times, it was the fastest to solve an instance.
\item[VBS2]
``Time aware, but proportional'':
A solver $S$ solving an instance $I$ in time $T^S_I$ accrues 
the following fraction of a point for solving $I$:
$T^\mathit{VBS}_I/T^S_I$, where $T^\mathit{VBS}_I$ is the solution time of the best solver on $I$.
\item[VBS3]
``Split the point for solving'':
We award each solver $S$ solving an instance $I$ the fraction $1/|\mathcal{S}_I|$ of points, where
$\mathcal{S}_I$ is the set of solvers solving $I$.
\end{description}
We remark that the sum of VBS1 points, as well as VBS3 points, computed across all the solvers
is equal to the number of instances solved by at least one solver (later denoted \emph{total}).
This is obvious for VBS1, as exactly one solver scores a point for solving an instance.
In the case of VBS3, where we discard the information about the solution times, 
we evenly split the one point reward for solving an instance to those solvers which were successful on it.

@@

Table~\ref{tab:vbsMainALL} renders the just-described three metrics applied 
to the full results of the Main track. We can see that the respective leaderboards 
are generally dominated by \solver{Kissat} and its configurations.
VBS1 tells us that \solver{Kissat-unsat} was most often the fastest solver,
in particular on \SI{11.5}{\percent} of all the solved instances.

@@

As can be seen from the ``contributes'' column, the presence of \solver{f2trc-DL} in the schedule is not necessary.
% The following three lines could be skipped without much harm:
All the 15 instances this solver solves under 76 seconds were already covered by the preceding three solvers.
This result, however, does not signify a bug, as Z3 was not asked to produce a schedule with a minimal number of
participating solvers.
Indeed, allowing any other solver to run for the 76 ``wasted'' seconds would not increase the overall total.
